\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-05 paper.qmd
Change uMAp to UMAP, add TriMAP to sentence

The parameter vector, $\vec{\theta}$, depends on the choice of $g$, and can be considered part of 'model fitting' in the traditional sense. Common choices for $g$ include tSNE, uMAP, PACMAP, or PHATE, although in theory any function that maps the entire space $\mathbb{R}^p$ to a subset of $\mathbb{R}^k$ is suitable. Any input requirements for the data (such as normalisation, or preprocessing through the use of PCA or similar) is considered part of the function $g$.

@@

The final step of the algorithm is _lifting_ the \kD model back to \pD, completing the 'model-in-data-space' picture. For this, define the set $H^k$ to be the set of points that belong to centroid $k$. That is, $H^k = \{ y \; | \; g(y) = (h_x^k, h_y^k)\}$. We use the \pD Euclidean mean of the points in $H^k$ to map the centroid $(h_x^k, h_y^k)$ to a point in \pD. Let the $i$-th component of the \pD mean be

>>>>

The parameter vector, $\vec{\theta}$, depends on the choice of $g$, and can be considered part of 'model fitting' in the traditional sense. Common choices for $g$ include tSNE, UMAP, PHATE, TriMAP, or PaCMAP, although in theory any function that maps the entire space $\mathbb{R}^p$ to a subset of $\mathbb{R}^k$ is suitable. Any input requirements for the data (such as normalisation, or preprocessing through the use of PCA or similar) is considered part of the function $g$.

@@

The final step of the algorithm is _lifting_ the \kD model back to \pD, completing the *model-in-the-data-space* picture. For this, define the set $H^k$ to be the set of points that belong to centroid $k$. That is, $H^k = \{ y \; | \; g(y) = (h_x^k, h_y^k)\}$. We use the \pD Euclidean mean of the points in $H^k$ to map the centroid $(h_x^k, h_y^k)$ to a point in \pD. Let the $i$-th component of the \pD mean be

### 2024-04-05 paper.tex
Change uMAp to UMAP, add TriMAP to sentence

The parameter vector, \(\vec{\theta}\), depends on the choice of \(g\),
and can be considered part of `model fitting' in the traditional sense.
Common choices for \(g\) include tSNE, uMAP, PACMAP, or PHATE, although
in theory any function that maps the entire space \(\mathbb{R}^p\) to a
subset of \(\mathbb{R}^k\) is suitable. Any input requirements for the
data (such as normalisation, or preprocessing through the use of PCA or
similar) is considered part of the function \(g\).

@@

The final step of the algorithm is \emph{lifting} the \kD model back to
\pD, completing the `model-in-data-space' picture. For this, define the
set \(H^k\) to be the set of points that belong to centroid \(k\). That
is, \(H^k = \{ y \; | \; g(y) = (h_x^k, h_y^k)\}\). We use the
\pD Euclidean mean of the points in \(H^k\) to map the centroid
\((h_x^k, h_y^k)\) to a point in \pD. Let the \(i\)-th component of the
\pD mean be

>>>>

The parameter vector, \(\vec{\theta}\), depends on the choice of \(g\),
and can be considered part of `model fitting' in the traditional sense.
Common choices for \(g\) include tSNE, UMAP, PHATE, TriMAP, or PaCMAP,
although in theory any function that maps the entire space
\(\mathbb{R}^p\) to a subset of \(\mathbb{R}^k\) is suitable. Any input
requirements for the data (such as normalisation, or preprocessing
through the use of PCA or similar) is considered part of the function
\(g\).

@@

The final step of the algorithm is \emph{lifting} the \kD model back to
\pD, completing the \emph{model-in-the-data-space} picture. For this,
define the set \(H^k\) to be the set of points that belong to centroid
\(k\). That is, \(H^k = \{ y \; | \; g(y) = (h_x^k, h_y^k)\}\). We use
the \pD Euclidean mean of the points in \(H^k\) to map the centroid
\((h_x^k, h_y^k)\) to a point in \pD. Let the \(i\)-th component of the
\pD mean be
